On the use of relative brain size - supplemental materials

### 2022-04-18 supplemental materials.Rmd
Updating all pdfs.

---
title: "On the use of relative brain size - supplemental materials"
author: "Simeon Q. Smeele $^{1,2,3}$"
date: "April 2022"
output:
  pdf_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
---

@@

@@

### Case I: relative brain size as response variable

@@

```{r plot response-20, echo=FALSE, out.width = "50%", fig.cap= "Model with sample size 20. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_20)
```

```{r plot response-1000, echo=FALSE, out.width = "50%", fig.cap= "Model with sample size 1000. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_1000)
```

### Case II: relative brain size as predictor variable

@@

```{r plot predictor-20, echo=FALSE, out.width = "72%", fig.cap= "Model with sample size 20. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model (SEM) with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_20)
```

```{r plot predictor-1000, echo=FALSE, out.width = "72%", fig.cap= "Model with sample size 1000. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model (SEM) with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_1000)
```

### Case I: relative brain size as response variable

@@

```{r plot response-informative, echo=FALSE, out.width = "50%", fig.cap= "Model with informative priors. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_informative)
```

```{r plot response-vague, echo=FALSE, out.width = "50%", fig.cap= "Model with vague priors. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_vague)
```

### Case II: relative brain size as predictor variable

@@

```{r plot predictor-informative, echo=FALSE, out.width = "72%", fig.cap= "Model with informative priors. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model (SEM) with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_informative)
```

```{r plot predictor-vague, echo=FALSE, out.width = "72%", fig.cap= "Model with vague priors. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model (SEM) with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_vague)
```

>>>>

---
title: "On the use of relative brain size - supplemental materials"
author: "Simeon Q. Smeele $^{1,2,3}$"
date: "April 2022"
output:
  pdf_document: default
header-includes:
- \usepackage{lineno}
- \linenumbers
- \renewcommand{\figurename}{Figure S}
- \makeatletter
- \def\fnum@figure{\figurename\thefigure}
- \makeatother
- \usepackage{setspace}
- \doublespacing
editor_options:
  chunk_output_type: console
bibliography: bibliography.bib
---

@@

\pagebreak

@@

@@

```{r plot response-20, echo=FALSE, out.width = "45%", fig.cap= "Model with sample size 20. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_20)
```

```{r plot response-1000, echo=FALSE, out.width = "45%", fig.cap= "Model with sample size 1000. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_1000)
```

@@

```{r plot predictor-20, echo=FALSE, out.width = "65%", fig.cap= "Model with sample size 20. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model  with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_20)
```

```{r plot predictor-1000, echo=FALSE, out.width = "65%", fig.cap= "Model with sample size 1000. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model  with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_1000)
```

@@

```{r plot response-informative, echo=FALSE, out.width = "45%", fig.cap= "Model with informative priors. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_informative)
```

```{r plot response-vague, echo=FALSE, out.width = "45%", fig.cap= "Model with vague priors. Parameter estimates from the linear model and Bayesian linear model with brain size as response variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_response_vague)
```

@@

```{r plot predictor-informative, echo=FALSE, out.width = "65%", fig.cap= "Model with informative priors. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model  with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_informative)
```

```{r plot predictor-vague, echo=FALSE, out.width = "65%", fig.cap= "Model with vague priors. Parameter estimates from the linear model, Bayesian linear model and Bayesian strucutral equation model  with relative brain size as predictor variable. Dashed grey line is the true value. Orange density plots are normal distributions based on the mean and SE from the linear model. Purple and green density plots are the posterior distributions from the Bayesian models."}
knitr::include_graphics(path_pdf_predictor_vague)
```
